---
title: "Building a Linear Regression Model to Predict Song's Valence (Not finished)"
author: "Srey Sea"
date: "6/25/2020"
output: github_document
---

In this project, I will create a linear regression model to predict a song's valence. Caution--the model obtained may or not be a good model for this prediction. The data is provided by Spotify and a Python script was created and used to collect the data in a .csv file.

Loading the songs dataset.

```{r}
mydata = read.csv("dataset.csv")
attach(mydata)
```

First, parameters, or the independent variables, need to be chosen to be used in the model.

The dataset has the following parameters:
```{r}
library(broom)
names(mydata)
```

The method of the **best subsets regression with adjusted R$^2$** will be used to select the independent variables. The model with the highest adjusted R$^2$ values and the lowest MSE value is deemed the best model. Below shows that model #6 is the best model, so, danceability, energy, speechiness, acousticness, liveness, and duration_ms are the appropriate predictors to be used.

```{r}
library(leaps)
n = length(mydata[,1])
mod = regsubsets(cbind(danceability,energy,key,loudness,mode,speechiness,
                       acousticness,instrumentalness,liveness,tempo,
                       duration_ms,time_signature),valence)
summary.mod = summary(mod)
rss = summary.mod$rss
mses = c(rss[1]/(n-2),rss[2]/(n-3),rss[3]/(n-4),rss[4]/(n-5),rss[5]/(n-6),
         rss[6]/(n-7),rss[7]/(n-8),rss[8]/(n-9))
mses
summary.mod$adjr2
summary.mod$which
```

Interaction terms should be considered. Using a correlation heatmap (the tutorial to create a correlation heatmap can be found here)

```{r}
mydata2 = mydata[,c(4,5,9,10,12,20)]
cormat = round(cor(mydata2),2)
library(reshape2)
melted_cormat = melt(cormat)
get_upper_tri = function(cormat){
  cormat[lower.tri(cormat)]<- NA
  return(cormat)
}

upper_tri = get_upper_tri(cormat)

melted_cormat = melt(upper_tri, na.rm = TRUE)
# Heatmap
library(ggplot2)
ggheatmap = ggplot(data = melted_cormat, aes(Var2, Var1, fill = value))+
  geom_tile(color = "white")+
  scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
                       midpoint = 0, limit = c(-1,1), space = "Lab", 
                       name="Pearson\nCorrelation") +
  theme_minimal()+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, 
                                   size = 12, hjust = 1))+
  coord_fixed()

ggheatmap + 
  geom_text(aes(Var2, Var1, label = value), color = "black", size = 4) +
  theme(
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    panel.grid.major = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    axis.ticks = element_blank(),
    legend.justification = c(1, 0),
    legend.position = c(0.6, 0.7),
    legend.direction = "horizontal")+
  guides(fill = guide_colorbar(barwidth = 7, barheight = 1,
                               title.position = "top", title.hjust = 0.5))